### 2022-01-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d02a7d6914473de70559174e284da8ec696ee1ca 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@bc2a1c88fcd2e4d7cf6f074fd89d176be6591fca 🚀

\begin{enumerate}
    \item Metawebs, i.e.~networks of potential interactions within a
species pool, are a powerful abstraction to understand how large-scales
species interaction networks are structured.%
    \item Because metawebs are typically expressed at large spatial and
taxonomic scales, assembling them is a tedious and costly process;
predictive methods can help circumvent the limitations in data
deficiencies, by providing `draft' metawebs.%
    \item One way to improve the predictive ability is to maximize the
information used for prediction, by using graph embeddings rather than
the list of species interactions. Graph embedding is an emerging field
in machine learning that holds great potential for ecoloigcal problems.%
    \item In this perspective, we outline how the challenges associated
with infering metawebs line-up with the advantages of graph embeddings;
furthermore, because metawebs are inherently spatial objects, we discuss
how the choice of the species pool has consequences on the reconstructed
network, but also embeds hypotheses about which human-made boundaries
are ecologically meaningful.%
\end{enumerate}

@@

Graph embedding fig.~\ref{fig:embedding} is a varied family of machine
learning techniques aiming to transform nodes and edges into a vector
space (Arsov \& Mirceva, 2019), usually of a lower dimension, whilst
maximally retaining key properties of the graph (Yan et al., 2005).
Ecological networks are an interesting candidate for the widespread
application of embeddings, as they tend to posess a shared sstructural
backbone (Mora et al., 2018), which hints at structural invariants that
can be revealed a lower dimensions. Indeed, previous work by Eklöf et
al. (2013) suggests that food webs are inherently low-dimensional
objects, and can be adequately represented with less than ten
dimensions. Simulation results by Botella et al. (2022) suggest that
there is no best method to identify architectural similarities between
networks, and that multiple approaches need to be tested and compared to
the network descriptor of interest. This matches with previous, more
general results on graph embedding, which suggest that embedding
algorithm choice matters for the results (Goyal \& Ferrara, 2018). In
tbl.~\ref{tbl:methods}, we present a selection of common graph
embeddings methods, alongside examples of their use to predict species
interactions (when they have been used this way).

@@

The second series of problems are related to determining which area
should be used to infer the new metaweb in, as this determines the
species pool that must be used. Metawebs can be constructed by assigning
interactions in a list of species within geographic boundaries. The
upside of this approach is that information at the country level is
likely to be required for biodiversity assessments, as countries set
goals at the national level (Buxton et al., 2021), and as quantitative
instruments are designed to work at these scales (Turak et al., 2017);
specific strategies are often enacted at smaller scales, nested within a
specific country (Ray et al., 2021). But there is no guarantee that
these boundaries are meaningful. In fact, we do not have a satisfying
answer to the question of ``where does a food web stop?''; the most
promising solutions involve examining the spatial consistency of network
area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
2018, 2019, 2021), which is impossible in the absence of enough
information about the network itself. This suggests that infered metaweb
should be futher downscaled to allow \emph{a posteriori} analyses.

>>>>

\begin{enumerate}
    \item Metawebs, i.e.~networks of potential interactions within a
species pool, are a powerful abstraction to understand how large-scales
species interaction networks are structured.%
    \item Because metawebs are typically expressed at large spatial and
taxonomic scales, assembling them is a tedious and costly process;
predictive methods can help circumvent the limitations in data
deficiencies, by providing `draft' metawebs.%
    \item One way to improve the predictive ability is to maximize the
information used for prediction, by using graph embeddings rather than
the list of species interactions. Graph embedding is an emerging field
in machine learning that holds great potential for ecological problems.%
    \item In this perspective, we outline how the challenges associated
with infering metawebs line-up with the advantages of graph embeddings;
furthermore, because metawebs are inherently spatial objects, we discuss
how the choice of the species pool has consequences on the reconstructed
network, but also embeds hypotheses about which human-made boundaries
are ecologically meaningful.%
\end{enumerate}

@@

Graph embedding fig.~\ref{fig:embedding} is a varied family of machine
learning techniques aiming to transform nodes and edges into a vector
space (Arsov \& Mirceva, 2019), usually of a lower dimension, whilst
maximally retaining key properties of the graph (Yan et al., 2005).
Ecological networks are an interesting candidate for the widespread
application of embeddings, as they tend to possess a shared structural
backbone (Mora et al., 2018), which hints at structural invariants that
can be revealed a lower dimensions. Indeed, previous work by Eklöf et
al. (2013) suggests that food webs are inherently low-dimensional
objects, and can be adequately represented with less than ten
dimensions. Simulation results by Botella et al. (2022) suggest that
there is no best method to identify architectural similarities between
networks, and that multiple approaches need to be tested and compared to
the network descriptor of interest. This matches with previous, more
general results on graph embedding, which suggest that embedding
algorithm choice matters for the results (Goyal \& Ferrara, 2018). In
tbl.~\ref{tbl:methods}, we present a selection of common graph
embeddings methods, alongside examples of their use to predict species
interactions (when they have been used this way).

@@

The second series of problems are related to determining which area
should be used to infer the new metaweb in, as this determines the
species pool that must be used. Metawebs can be constructed by assigning
interactions in a list of species within geographic boundaries. The
upside of this approach is that information at the country level is
likely to be required for biodiversity assessments, as countries set
goals at the national level (Buxton et al., 2021), and as quantitative
instruments are designed to work at these scales (Turak et al., 2017);
specific strategies are often enacted at smaller scales, nested within a
specific country (Ray et al., 2021). But there is no guarantee that
these boundaries are meaningful. In fact, we do not have a satisfying
answer to the question of ``where does a food web stop?''; the most
promising solutions involve examining the spatial consistency of network
area relationships (Fortin et al., 2021; see \emph{e.g.} Galiana et al.,
2018, 2019, 2021), which is impossible in the absence of enough
information about the network itself. This suggests that inferred
metaweb should be further downscaled to allow \emph{a posteriori}
analyses.
